Investigating Determinism of Gaming Engines for Autonomous Vehicle Verification

### 2020-03-16 paper/cav_determinisim_main.tex
changed 1cm threshold reason

The user must specify the level of variance acceptable for their application which is used as a threshold for deterministic execution. In our case study, Section~\ref{s:case-study}, a threshold of $1cm$ was chosen for our given application which reflects the scale at which repeatability of simulation execution is required. This value is sufficiently small to allow accurate \textit{assertion checking} of autonomous vehicles in urban environments [ref] but a larger value may be acceptable for non-urban environments, e.g. motorway or highway. Similarly, the threshold value should not be so small as to fail with minor computational bottlenecks, e.g. $1\mu m$.

Depending on the number of repeated tests and the average deviation reported from the experiment, a maximum rather than average may be required if the results are close to the user-specified threshold. This is to ensure that an outlier data-point is not hidden in the average of $n$-tests

@@

\subsection{Output and Analysis}
The output for each experiment can be summarised as the maximum variance of any actor over the repeated tests. This value can be analysed against the different scenarios or settings that have been identified as potential sources of simulation variance. These values can then be assessed against the user-defined \textit{deterministic threshold} to determine if the simulation is deterministic or not.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummaryV2.pdf}
    \caption{Summary of results showing maximum deviation for each scenario against different resource utilisation levels. Tests 5 and 6 overlap having almost identical results.}
    \label{ExperimentsStressSummary}
\end{figure}

@@

>>>>

The user must specify the level of variance acceptable for their application which is used as a threshold for deterministic execution. In our case study, Section~\ref{s:case-study}, a threshold must be chosen for our given application which reflects the scale at which repeatability of simulation execution is required. This value must be sufficiently small to allow accurate \textit{assertion checking} of the ego vehicle in the environment but a larger value may be acceptable for non-urban environments, e.g. motorway or highway. Similarly, the threshold value should not be so small as to fail with minor computational bottlenecks, e.g. $1\mu m$. Two autonomous vehicle projects this group are involved in, Robopilot and Capri, are looking at urban mobility and last mile delivery solutions which are predominantly concerned with urban environments rather than highway or motorway scenarios. Because of this, a deterministic threshold of $1m$ is insufficient when considering potentially dangerous close passing of cyclists and pedestrians and therefore a threshold of $1cm$ is more suitable.

% Depending on the number of repeated tests and the average deviation reported from the experiment, a maximum rather than average may be required if the results are close to the user-specified threshold. This is to ensure that an outlier data-point is not hidden in the average of $n$-tests.

@@

\subsection{Output and Analysis}
The output for each experiment can be summarised as the \textit{maximum variance} of any actor over the $n-$repeated tests. The maximum variance is chosen to indicate the worst case rather than an average which could hide outlier data points when a high number of repeated tests are performed. This value can be analysed against the different scenarios or settings that have been identified as potential sources of simulation variance. These values can then be assessed against the user-defined \textit{deterministic threshold} to determine if the simulation is deterministic or not.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummaryV3.pdf}
    \caption{Summary of results showing maximum deviation for each scenario against different resource utilisation levels. Tests 5 and 6 overlap having almost identical results.}
    \label{ExperimentsStressSummary}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummaryV4.pdf}
    \caption{Summary of total mean deviation for the different tests runs plotted against the different CPU + GPU stresses.}
